---
title: "Spatial Figures Peer Review"
output: html_document
---
# Michelle Lin

## Problem 1

Create the following figure, using the data included in the R Markdown file.

```{r problem_1_data,include=FALSE}
options(repos = list(CRAN="http://cran.rstudio.com/"))
library(tidyverse)
library(maps)

####make some data for painting the map

my_world_map <- map_data("world")

countries <- unique(my_world_map$region)

set.seed(987)
some_data_values <- data.frame(

  "region"=countries,
  
  "Score"=runif(252,0,100))

```

```{r problem_1,echo=FALSE,message=FALSE}

##library
library(ggplot2)

##Join data
map_data <- left_join(my_world_map, some_data_values, by = "region")

#plot
ggplot() + geom_polygon(data = map_data, aes(x = long, y = lat, group = group, fill = Score)) + scale_fill_distiller(palette = 5)
```

## Problem 2

Create the following figure, using the data included in the R Markdown file.


```{r problem_2_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK
set.seed(15)
Measurement<-rnorm(32,50,1)
```


```{r solution_p2,echo=FALSE,message=FALSE}

##library
library(ggplot2)
library(maps)

#make dataframes for Costa Rica, Panama, Nicaragua
central_america <- filter(my_world_map, region == "Costa Rica" | region == "Panama" | region == "Nicaragua")

#input city data
my_cities <- maps::world.cities

central_amer_city <- filter(my_cities, country.etc == "Panama" | country.etc == "Costa Rica" | country.etc == "Nicaragua", pop > 40000)

#attach measurement data

central_amer_city <- central_amer_city %>% add_column(Measurement)

#plot
ggplot(data = central_america, mapping = aes(x = long, y = lat, group = group)) + geom_polygon(colour = "black", fill = "white") + geom_point(data = central_amer_city, aes(x = long, y = lat, group = NULL, color = Measurement), size = 5) + scale_color_distiller(palette = 7)
```

## Problem 3

Create the following figure, using the data included in the R Markdown file.

Note that the code in the .rmd file will import a set of simple features data for South America. Make sure you install any necessary packages. 

```{r problem_3_data,include=FALSE}

#####INSTALL THESE PACKAGES IF NECESSARY
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(rgeos)

####DO NOT MODIFY
s_america<-ne_countries(scale="medium",continent='south america',returnclass="sf")

```

```{r problem3,echo=FALSE}

#library
library(ggplot2)
library(maps)

#plot
ggplot() + geom_sf(data = s_america, aes(fill = pop_est)) + scale_fill_distiller(palette = 10)

```


